```{r}
library(kableExtra)
library(tidyverse)
library(lme4)
library(ggspatial)
```

input our data
```{r}
llp <- read_csv("../light_project/data-raw/leaf_light_project.csv")
llp[1:5,] %>% kbl() %>% kable_styling()
```

Then we calculate LMA and show our samples location away from the light.
```{r}
llp1 <- llp |>mutate(LMA = dry_weight/(disc*pi*(0.005)^2))
llp1$species[llp1$species =="Melastoma_candidum"] <-  'Melastoma candidum'
llp1$species[llp1$species =="Colocasia_gigantea"] <- 'Colocasia gigantea'
llp2 <- llp1 |> 
  mutate(x_loc = Distance*cos(angel*pi/180))|>
  mutate(y_loc = Distance*sin(angel*pi/180))
```

```{r sp1}
llp2 |> filter(species == "Melastoma candidum")|>
  ggplot(aes(x_loc, y_loc, color = LMA, size = 7))+
  guides(size = "none")+
  scale_color_gradient(low = "#43ff2a",high = "#105cff")+
  coord_fixed(xlim = c(-10,10), ylim = c(-10,10))+
  geom_hline(yintercept = 0,linetype="dotted")+
  geom_vline(xintercept = 0,linetype="dotted")+
  facet_wrap(vars(species),nrow = 1,strip.position = "top")+
  geom_point(shape =16)+
  labs(x = "", y = "")+
  theme(strip.text = element_text(face = "italic",size = 14),legend.position = c(0.9,0.5),legend.key.size = unit(35,"pt"))

```


```{r sp1}
llp2 |> filter(species == "Colocasia gigantea")|>
  ggplot(aes(x_loc, y_loc, color = LMA, size = 7))+
  guides(size = "none")+
  scale_color_gradient(low = "#43ff2a",high = "#105cff")+
  coord_fixed()+
  geom_hline(yintercept = 0,linetype="dotted")+
  geom_vline(xintercept = 0,linetype="dotted")+
  facet_wrap(vars(species),nrow = 1,strip.position = "top")+
  geom_point(shape =16)+
  labs(x = "", y = "")+
  theme(strip.text = element_text(face = "italic",size = 14),legend.position = c(0.9,0.5),legend.key.size = unit(35,"pt"))

```











ggplot(aes(x_loc, y_loc, color = LMA, size = 7))+
  guides(size = "none")+
  scale_color_gradient(low = "#43ff2a",
  high = "#105cff")+
  coord_fixed()+
  geom_hline(yintercept = 0,linetype="dotted")+
  geom_vline(xintercept = 0,linetype="dotted")+
  geom_point(shape =16)+
  facet_wrap(vars(species),nrow = 2,strip.position = "top")+
  labs(x = "", y = "")+
  theme(strip.text = element_text(face = "italic",size = 14))