---
title: Light project soil analysis 
author: Cong
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
#rmdformats::material
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: TRUE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
---

```{r}
library(tidyverse)
library(ggpubr)
```

```{r}
soil <- read.csv("../data-raw/soil_nutrients.csv")
soil
```

Here are the funcitons we'll use to calculate the ratio and mean value.
```{r}
ratio <- function(data) {
     t <- data[2,]/data[1,]
     names(t) <- c("ratio_C","ratio_N","ratio_P","noyear")
     t
}

ave <- function(data) {
  tt <- map(data,mean)
  names(tt) <- c("ave_C","ave_N", "ave_P")
  as_tibble(tt)
}
```

Here data clean thing:
```{r}
t <- as_tibble(soil) %>% select(-Tag) %>%
      group_by(Plot,Distance) %>% nest() %>% 
      mutate(Ratio = map(data, ratio))%>%
      unnest(cols = c(data,Ratio)) %>% 
      select(-noyear)%>%ungroup%>%
      mutate(Plot = as.character(Plot))%>%
      mutate(Distance = as.character(Distance))
t
```

For example, showing the total carbon change between 2019 and 2022 under ALAN among 5 plots:
```{r}
t %>%filter(Distance == 0) %>% 
    ggplot(., aes(x = Year, y = T.C, color = Plot))+
    geom_point(size = 4)+geom_line(size = 1.5)+ ggtitle("Under ALAN")
```

Here shows all the change of total carbon among 5 plots:
```{r}
t %>%ggplot(., aes(x = Year, y = T.C, color = Plot, linetype = Distance))+
       geom_line(size = 1.5) +
       geom_point(size = 4, shape = 17) 
```

Here is total soil Nitrogen comparison bewteen 2019 and 2022.
```{r}
t %>% mutate(Year = as.character(Year)) %>%ggplot(., aes(x = Year,y = T.N, group  = Year))+
      geom_boxplot()
```

Here list total C,N,P changing rate under ALAN and 10m away from light.
```{r}
p1 <- t %>% ggplot(.,aes(x = Distance, y = ratio_C, shape = Plot))+ geom_point(size = 8)
p2 <- t %>% ggplot(.,aes(x = Distance, y = ratio_N, shape = Plot))+ geom_point(size = 8)
p3 <- t %>% ggplot(.,aes(x = Distance, y = ratio_P, shape = Plot))+ geom_point(size = 8)
ggarrange(p1,p2,p3, nrow = 1, common.legend = T, legend = "right")
```

Here list total C,N,P changing rate under ALAN and 10m away from light of my experiments plots.
```{r}
p1 <- t %>% filter(Plot == c(2,5))%>% ggplot(.,aes(x = Distance, y = ratio_C, shape = Plot))+ geom_point(size = 8)
p2 <- t %>% filter(Plot == c(2,5))%>% ggplot(.,aes(x = Distance, y = ratio_N, shape = Plot))+ geom_point(size = 8)
p3 <- t %>% filter(Plot == c(2,5))%>% ggplot(.,aes(x = Distance, y = ratio_P, shape = Plot))+ geom_point(size = 8)
ggarrange(p1,p2,p3,nrow = 1, common.legend = T,heights = 0.8)
```





