---
title: "Leaf-light-project"
author: "cong"
date: "2021/12/23"
output:
  html_document:
    toc: yes
    number_section: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  fig.align = 'center',
  fig.show = "hold"
)
```

# Background
  The big light project puts a LED light into old-growth, secondary and man made forest(rubber tree forest) separetely, which shines at night. We rekon it as a long term disturbance to forest which has continued more than one year. Now we want to know whether this disturbance would effect the understory or not.
  
## Our hypothesis 
   1) Prolong the light time may effect the nutrition circulation of understory
   2) LED light attracts insects and insects dead may increase soil nitrogen, then effect the nutrition circulation of understory.

## Place and species I choosed 
We choose man made forest, for simulating the street tree
and species Colocasia_gigantea and Melastoma_candidum

## method
we punch leaf using leaf-disc to measure leaf nutrition.

# Data Exploration

the pacakges we'll use:
```{r}
library(kableExtra)
library(tidyverse)
library(lme4)
```

input our data
```{r}
llp <- read_csv("../data-raw/leaf_light_project.csv")
llp[1:5,] %>% kbl() %>% kable_styling()
```

Then we calculate LMA and show our samples location away from the light.
```{r}
llp1 <- llp |>mutate(LMA = dry_weight/(disc*pi*(0.005)^2))
llp1 |> 
  mutate(x_loc = Distance*cos(angel*pi/180))|>
  mutate(y_loc = Distance*sin(angel*pi/180))|>
  ggplot(aes(x_loc, y_loc, size = LMA))+
  geom_point(shape =17)+
  facet_grid(cols = vars(species))+
  theme_bw()

```
(Notation: coordinate (0,0) is where the light is.)


Next, because we want to know whether light give an effect to understory, so we consider a graph between LMA and Distance away from the light which is on behalf of the gradient of light strength.
```{r}
llp1 |> 
  filter(Plot == 2) |>
ggplot(aes(x = Distance, y = LMA))+
  geom_point()+
  labs(title = "LMA_Colocasia_gigantea")+
  theme_bw()
```


```{r}
llp1 |>
  filter(Plot == 5) |>
ggplot(aes(x = Distance, y = LMA))+
  geom_point()+
   labs(title = "LMA_Melastoma_candidum")+
  theme_bw()
```

(We see there can be a negative correlation between LMA and Distance, while we can't simply draw the conclusion based on that, instead we add canopy openness into our consideration. )


```{r}
llp1|> 
  ggplot(aes(x = LMA))+
  facet_grid(cols = vars(species))+
  geom_histogram()
```

# Data Mining

```{r}
mod <- lmer(data = llp1, formula = LMA ~ log(Distance)*log(canopy_openness)+(1|species))
summary(mod)
```


# stan

## example

```{r, message=FALSE}
library(rstan)
library(bayesplot)
rstan::rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores()) # Run on multiple cores
```

Data for Melastoma_candidum

```{r}
sp1 <- llp1 |>
  filter(species == "Melastoma_candidum")

x <- cbind(1,
            log(1/(sp1$Distance)^2) |> scale(),
            scale(sp1$canopy_openness))

x <- cbind(x, x[,2] * x[,3])

list_d <- list(
  N = nrow(sp1),
  J = sp1$individual |> unique() |> length(),
  K = 4,
  ind = sp1$individual,
  x = x,
  y = log(sp1$LMA))
```


#### Mathematical model {-}

Main likelihood functions:
$$
y_{i,j} \sim \mathcal{N}(\mu_{i,j}, \sigma)  \\
\mu_{i,j} = \boldsymbol{X} \cdot \boldsymbol{\beta} + \phi_j\\
\phi_j \sim \mathcal{N}(0, \tau)
$$

where,

- $y_{i,j}$ is log(LMA) of leaf disc *i* of individual *j*,

- $\sigma$ is the standard deviation of the model,

- $\boldsymbol{X}$ is an $n \times 4$ matrix with intercepts, distance, canopy_openness and the interaction between distance and canopy_openness,

- $\boldsymbol{\beta}$ is a coefficient vector of size 4 (intercepts, distance, canopy_openness and the interaction between distance and canopy_openness),

- $\phi_j$ is the vayring intercept for individuals,

- $\tau$ is the scaling parameter for individual effects

Prior:

- we usually use weakly informative priors and we don't use non-informative
  prirors such as unif(0, 1000).

$$
\boldsymbol{\beta} \sim \mathcal{N}(0, 5) \\
$$

Hyperprior:

- Half-cauchy works best for the scaling parameters for varying intercepts

$$
\boldsymbol{\tau} \sim \text{Half-Caucy}(0, 2.5) \\
$$


In reality, we use a lot of tricks to make the above model works better.
For example, we do not try to fit the individual effects directly, but instead, we fit a latent Gaussian variable from which we can recover the individual effects.

$$
\phi_j  \sim \mathcal{N}(0, \tau)
$$

cab be rewritten as:

$$
\phi_j =  \tau \cdot \tilde{\phi_j} \\
\tilde{\phi_j} \sim \mathcal{N}(0, 1) \\
\tau \sim \text{Half-cauchy}(0, 2.5)\\
$$


A Half-cauchy distribution can be also represented using the tangent function
and an uniform distribution:

$$
\boldsymbol{\tau} = 2.5 \times tan(\boldsymbol{\tilde{\tau}}) \\
\boldsymbol{\tilde{\tau}} \sim \mathcal{U}(0, \pi / 2)
$$


```{r, eval=TRUE }
model <- rstan::stan_model("../stan/model.stan")
```

```{r, collapse=FALSE, comment = ""}
writeLines(readLines("../stan/model.stan"))
```

```{r, eval=TRUE}
fit <- rstan::sampling(model,
            data = list_d,
            verbose = TRUE,
            iter = 2000,
            warmup = 1000,
            thin = 1,
            chains = 4,
            refresh = 200,
            seed = 123)
```

```{r}
summary(fit)$summary
```

95% CI

- beta[1,1] is the intercept which is not showing the figure.

```{r}
beta_name <- paste0("beta[", 2:4, ",1]")
mcmc_areas(fit,
           pars = beta_name,
           prob = 0.95)
```

**NO EFECT!**


Data for Colocasia_gigantea
```{r}
sp2 <- llp1 |>
  filter(species == "Colocasia_gigantea")

x1 <- cbind(1,
           log(1/(sp2$Distance) ^2)|> scale(),
           scale(sp2$canopy_openness))

x1 <- cbind(x1, x1[,2] * x1[,3])

list_d <- list(
  N = nrow(sp2),
  J = sp2$individual |> unique() |> length(),
  K = 4,
  ind = sp2$individual,
  x = x1,
  y = log(sp2$LMA))
```

```{r, eval=TRUE}
model1 <- rstan::stan_model("../stan/model.stan")
```

```{r, collapse=FALSE, comment = ""}
writeLines(readLines("../stan/model.stan"))
```

```{r, eval=TRUE}
fit1 <- rstan::sampling(model1,
                       data = list_d,
                       verbose = TRUE,
                       iter = 2000,
                       warmup = 1000,
                       thin = 1,
                       chains = 4,
                       refresh = 200,
                       seed = 123)
```

```{r}
summary(fit1)$summary
```

```{r}
beta_name <- paste0("beta[", 2:4, ",1]")
mcmc_areas(fit1,
           pars = beta_name,
           prob = 0.95)
```


So we can see for species Colocasia_gigantea the regression coefficients of distance and canopy openness are significant.

# Table the results
For species one "Melastoma_candidum", coefficients table.
```{r}

test <- summary(fit)$summary[2:4,] |> as_tibble()

quantile_interval <-  paste0("[",round(test$`2.5%`,4),", ",  round(test$`97.5%`,4),"]")

table_sp1 <- data.frame(
  "Parameters" = c(
                   "ALAN's effect",
                   "Daylight's effect",
                   "interaction"),
  "mean_value" = round(test$mean,4),
 quantile_interval 
)

table_sp1 %>%
  kbl(caption = "Coefficients table of species Melastoma_candidum") %>%column_spec(3,bold =  ifelse(test$`2.5%`*test$`97.5%`>0, "T","F"))%>% 
  kable_classic(full_width = F, html_font = "Cambria")

```

For species "Colocasia_gigantea", coefficients table.
```{r}
test1 <- summary(fit1)$summary[2:4,] |> as_tibble()

quantile_interval <-  paste0("[",round(test1$`2.5%`,4),", ",  round(test1$`97.5%`,4),"]")

table_sp2 <- data.frame(
  "Parameters" = c(
                   "ALAN's effect",
                   "Daylight's effect",
                   "interaction"),
  "mean_value" = round(test1$mean,4),
 quantile_interval 
)

table_sp2 %>%
  kbl(caption = "Coefficients table of species Colocasia_gigantea") %>%column_spec(3,bold =  ifelse(test1$`2.5%`*test1$`97.5%`>0, "T","F"))%>% 
  kable_classic(full_width = F, html_font = "Cambria")

```

#Put together

```{r}
rbind(table_sp1,table_sp2)|>
  kbl( caption = "Coefficients table") %>%
  kable_paper("striped", full_width = F) %>%
  column_spec(3,bold =c(ifelse(test$`2.5%`*test$`97.5%`>0, "T","F"),       ifelse(test1$`2.5%`*test1$`97.5%`>0, "T","F"))) %>% 
  pack_rows("Melastoma_candidum", 1, 3) %>%
  pack_rows("Colocasia_gigantea", 4, 6)

```

```{r}
table|>
  kbl( caption = "Coefficients table") %>%
  kable_paper("striped", full_width = F) %>%
  column_spec(4,bold =c(ifelse(test$`2.5%`*test$`97.5%`>0, "T","F"),       ifelse(test1$`2.5%`*test1$`97.5%`>0, "T","F"))) %>% 
  pack_rows("Melastoma_candidum", 1, 3) %>%
  pack_rows("Colocasia_gigantea", 4, 6)
```